---
title: "unobankproject"
author: "Arun Ranganathan"
date: "December 10, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Making credit risk modeling easier"}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
library(ggplot2)
library(knitr)
library(kableExtra)


opts_chunk$set(
  fig.path = 'figure/graphics-',
  cache.path = 'cache/graphics-',
  fig.align = 'center',
  external = TRUE,
  echo = TRUE,
  warning = FALSE,
  fig.pos = 'H'
  )
output <- opts_knit$get("rmarkdown.pandoc.to")
if (output=="html") opts_chunk$set(out.width = '400px', dpi=100) else
  opts_chunk$set(out.width='.6\\linewidth')

options(knitr.table.format = "latex")
```

Credit risk modeling is a complex task for Bank's. I created a set of functions that would make it easier for building models.

Here are some sample functions written for this package development exercise.

### Distributions

```{r}

pct_freq <- function(x) {
  tbl <- table(x)
  tbl_pct <- cbind(tbl, round(prop.table(tbl) * 100, 2))
  colnames(tbl_pct) <- c('Count', 'Percentage')
  knitr::kable(tbl_pct)
}

```

This function takes in a vector of values and create a frequency or distribution table and display the results in a knitr kable table format. Quick glance on distribution of variables gives us a good idea on how to deal with that variable.

```{r}

a<-rbind(sample(c(1:10),20, replace = T))
pct_freq(a)

```

### Variance inflation factor

Variance inflation factor is a measure of multicollinearity between variables. VIF can be used to remove highly collinear variables. When we have hundreds of variables it is hard to remove variables one by one. vif_glmrepeat function will remove highly collinear variables that are above threshold one by one. Finally we will have variables that are below our threhold.





